### 2017-07-13 src/5_3_Proposal.tex
falta revisar algoritmos

Both VECM and VAR model parameters are obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

Our proposal is an online formulation of the VECM called Online VECM (OVECM)
based on consideration of only a sliding window of the historical data.  OVECM
introduces matrix optimizations in order to reduce the number of operations and
also takes into account the fact that cointegration vector space doesn't
experience large changes with small changes in the input data. Moreover, OVECM
uses RR instead of OLS to obtain VECM parameters. Our method is later tested using four
currency rates from the foreign exchange market with a frequency of 10 seconds.
Model efectiveness is focused on out-of-sample forecast rather than in-sample
fitting.  This criteria allows the OVECM prediction capability to be expressed
rather than just explaining data history. Our method performance is compared
with its optimal offline algorithm.

@@

On the other hand, getting cointegration vectors using Johansen method is also
an expensive procedure. However, since cointegration
vectors represent the long-run relationship between the time series, they
vary little in time. Our proposal obtains new cointegration vectors only when
this long-term relationship changes. This change is detected by tracking 
the Mean Absolute Percentage Error (MAPE) of the last $n$ in-sample forecasts.

@@

VECM($p$) for $l$ cointegrated variables has the following form:

\begin{equation}\label{eq:vecfull}
\Delta\mathbf{y}_t 
= \boldsymbol{\alpha\beta}^\top\mathbf{y}_{t-1} 
  + \sum_{i=1}^{p-1}\boldsymbol{\Phi}_i^*\,\Delta\mathbf{y}_{t-i}
  + \mathbf{c} + \boldsymbol{\epsilon}_t \qquad \forall t = p+1,\dots,N.
\end{equation}

Transposing each equation of the system (\ref{eq:vecfull}) we can write
the VECM($p$) model in block-matrix form as:
\begin{equation}\label{eq:vareq}
\mathbf{B} = 
\mathbf{A} \mathbf{X} + 
\mathbf{E} \, , 
\end{equation}
%
\noindent where $\mathbf{B}$ dimension is $((N-p)\times l)$, $\mathbf{A}$
dimension is $((N-p)\times(r+(p-1)l +1))$, $\mathbf{X}$ dimension is $((r+(p-1)l
+1)\times l)$, $\mathbf{E}$ dimension is $((N-p)\times l)$ and $r$ is the number
of cointegration vectors:
%
\begin{alignat}{3}
\mathbf{B}
&= \begin{bmatrix}
   \Delta\mathbf{y}_{p+1}^\top \\
   \Delta\mathbf{y}_{p+2}^\top \\
   \vdots \\
   \Delta\mathbf{y}_N^\top
   \end{bmatrix}
&\quad
\mathbf{X}
&= \begin{bmatrix}
   \boldsymbol{\alpha}^\top \\
   \boldsymbol{\Phi}_1^{*\top} \\
   \boldsymbol{\Phi}_2^{*\top} \\
   \vdots \\
   \boldsymbol{\Phi}_{p-1}^{*\top} \\
   \mathbf{c}^\top
   \end{bmatrix}
&\quad
\mathbf{E}
&= \begin{bmatrix}
   \boldsymbol{\epsilon}_{p+1}^\top \\
   \boldsymbol{\epsilon}_{p+2}^\top \\
   \vdots \\
   \boldsymbol{\epsilon}_N^\top \\
   \end{bmatrix}
\end{alignat}
\noindent and 
\begin{align}
\mathbf{A} 
&= \begin{pmat}[{....|}]
   \mathbf{y}_p^\top \boldsymbol{\beta} & \Delta \mathbf{y}_p^\top & \Delta\mathbf{y}_{p-1}^\top & \dots 
                    & \Delta\mathbf{y}_2^\top & 1 \cr
   \mathbf{y}_{p+1}^\top  \boldsymbol{\beta} &\Delta\mathbf{y}_{p+1}^\top & \Delta\mathbf{y}_p^\top & \dots
                       & \Delta\mathbf{y}_3^\top & 1 \cr
   \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \cr
   \mathbf{y}_{N-1}^\top  \boldsymbol{\beta} &\Delta\mathbf{y}_{N-1}^\top & \Delta\mathbf{y}_{N-2}^\top & \dots 
                       & \Delta\mathbf{y}_{N-p-1}^\top & 1 \cr
   \end{pmat}\, .
\end{align}
%Taking into account the error term $\mathbf{E}$, equation~(\ref{eq:vareq}) 
%can be solved with respect to $\mathbf{X}$ using the ordinary least
%squares estimation.
However, the number of rows of matrix $\mathbf{A}$ increases with the number of
observations $\mathbf{y}_t$. Our proposal considers only the most recent $L$
rows of matrices $\mathbf{A}$ and $\mathbf{B}$ defined as  $\mathbf{A}(t)$ and
$\mathbf{B}(t)$:

@@

Our proposal considers the following:

>>>>

VECM model parameters are traditionally obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

The proposal is to modify OVECM so it wan be an incremental algorithm and also
to use RR and its variant AAR instead of OLS. Therefore, three different
variations of OVECM using as a solver: OLS, RR and AAR will be compared.

@@

On the other hand, getting cointegration vectors using Johansen method is also a
computationally expensive procedure. However, since cointegration vectors
represent the long-run relationship between the time series, they vary little in
time. This proposal also include to obtain new cointegration vectors only when
this long-term relationship changes. This change is detected by tracking the
Mean Absolute Percentage Error (MAPE) of the last $n$ in-sample forecasts.

@@

VECM($p$) was defined in equation \ref{eq:vecfull} and its matrix form is:

\begin{equation}\label{eq:vareq}
\mathbf{B} = 
\mathbf{A} \mathbf{X} + 
\mathbf{E} \, , 
\end{equation}

\noindent where matrix $\mathbf{B}$ is defined in equation
\ref{eq:vecY}, matrix $\mathbf{X}$ is detailed in equation \ref{eq:vecX}, matrix
$\mathbf{E}$ in equation \ref{eq:vecE} and matrix $\mathbf{A}$ in equation \ref{eq:vecA}.

In the traditional VECM the number of rows of matrix $\mathbf{A}$ increases with the number of
observations $\mathbf{y}_t$. This proposal considers only the most recent $L$
rows of matrices $\mathbf{A}$ and $\mathbf{B}$ defined as  $\mathbf{A}(t)$ and
$\mathbf{B}(t)$:

@@

The proposal considers the following:
